\chapter*{Abstract} % Asterisk keeps it out of numerical numbering
\addcontentsline{toc}{chapter}{Abstract} % But adds it to the Table of Contents

In today’s digital era, verifying the authenticity of employee experience certificates re-
mains a challenge for organizations. Employers require a fast and cost-effective means
of confirming the qualifications of potential employees, but the current system still re-
lies on outmoded systems of manual confirmation, direct communication with previous
employers, or services from third-party organizations, and reliance on paper or easily pho-
tocopied documents. These traditional systems are not only time-consuming but are also
susceptible to deception and incorrect information. This thesis presents a blockchain sys-
tem to verify employee experience or service certificates through a consortium blockchain
and a proof-of-stake consensus algorithm. It is secure, tamper-evident, and decentralized
by presenting digitally encrypted and signed certificates on the blockchain presented by
previous employers. The former employer gives the decryption key and transaction ID to
the employee, and the employee gives the decryption key and transaction ID to the new
employer, who can verify the validity and integrity of the certificate on the blockchain.
Consortium blockchain simply gives verified and trusted employers the right to access
the network, as proof-of-stake provides secure and rapid consensus. Using the power of
blockchain theory, cryptographic encryption, and digital signatures, this thesis constructs
a modern, scalable, and tamper-evident employment confirmation process to enable indi-
viduals and trigger HR activity.

\vspace{0.5cm} % Adjust this value (e.g., 1cm, 2cm) to get the desired space

\noindent \textbf{Keywords:} \textit{Consortium Blockchain, Proof-of-Stake, Certificate Verification, Cryptography.}