\thispagestyle{plain}

{\centering \Large \textbf{ACKNOWLEDGEMENTS} \par}
\vspace{40pt} % Space between title and first paragraph

\noindent It is indeed a great pleasure to express my sincere thanks to my guide \textbf{\myguide}, Associate Professor, \mydept, \myinst, for his continuous support and guidance in this thesis. He was always there to listen and encourage me. He showed me different ways to approach a research problem and the need to be persistent to accomplish my goal. He inspired me to think through the problems and generate new ideas. I will always be grateful to him for his valuable supervision and guidance.

\noindent I would like to thank \textbf{\myhod} (Head of Department) and all the faculty members of Computer Science and Engineering, \myinst, for their valuable support and suggestions towards the research work.

\noindent I am grateful to my family members and friends for their constant support and motivation.

\noindent Last, but not least, I want to thank my parents for giving me life in the first place and for educating me. I would like to thank my family for their unconditional support and encouragement to pursue my interests. It is a pleasure to express my deepest gratitude to all those who inspired me in the successful completion of the project.

\vspace{1.5cm}

% This creates a block on the right, but the text inside stays left-aligned
\hfill
\begin{minipage}{0.3\textwidth}
    \textbf{\myname} \\
    \myrollno \\
    M.Tech. CSE \\
    IIT (ISM), Dhanbad \\
    Date: \myday\ \mymonth\ \myyear
\end{minipage}